Left-linear rules in adhesive categories

### 2024-02-11 icalp/fusione.tex
typos

\begin{example}
  \label{ex:adhesive}
  Every topos is adhesive~\cite{lack2006toposes}, thus in particular
  $\cat{Set}$ is adhesive. By the closure properties recalled before,
  every presheaf $[\cat{X},\cat{Set}]$ is adhesive and in particular
  the category $\cat{Graph} = [ E \rightrightarrows V, \cat{Set}]$ is
  adhesive where $E \rightrightarrows {V}$ is the two object category
  with two morphisms $s,t \colon{E} \to {V}$. In a similar way,
  various categories of hypergraphs can be shown to be adhesive, while
  the category $\cat{sGraphs}$ of simple graphs, i.e., graphs without
  parallel edges is quasi-adhesive, i.e.
  $\reg{(\cat{sGraphs})}$-adhesive.\todo{Add hierarchical graphs and term graphs\cite{castelnovo2023thesis,CastelnovoGM22}).}
\end{example}

@@

\subsection{A canonical form for  switch equivalences}

@@

\subsection{Proofs for \Cref{subsec:perm}}

@@

\subsubsection{Proofs for \Cref{subsec:3steps}}

@@

%%%%%%%%%%% NO NEED OF USELESS SHIFTS

>>>>

\begin{example}
  \label{ex:adhesive}
  Every topos is adhesive~\cite{lack2006toposes}, thus in particular
  $\cat{Set}$ is adhesive. By the closure properties recalled before,
  every presheaf $[\cat{X},\cat{Set}]$ is adhesive and in particular
  the category $\cat{Graph} = [ E \rightrightarrows V, \cat{Set}]$ is
  adhesive where $E \rightrightarrows {V}$ is the two object category
  with two morphisms $s,t \colon{E} \to {V}$. In a similar way,
  various categories of hypergraphs can be shown to be adhesive, while
  the category $\cat{sGraphs}$ of simple graphs, i.e., graphs without
  parallel edges is ?\todo{P: su simple graphs riusciamo a dire qualcosa? Non sono reg-adesivi, giusto?}, i.e.
  $\reg{(\cat{sGraphs})}$-adhesive.\todo{Add hierarchical graphs and term graphs\cite{castelnovo2023thesis,CastelnovoGM22}).}
\end{example}

@@

\subsection{A canonical form for  switch equivalences}
\label{subsec:canonical}

@@

\subsubsection{Proofs for \Cref{subsec:perm}}

@@

\subsubsection{Proofs for \cref{subsec:canonical}}

@@
